---
title: "arya-class-5-sst"
subtitle: "Arya Singh"
author: "Onkar Singh"
institute: "Shri Ram Global School"
date: "2021/11/20 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: inverse, center, middle

```{r , echo=FALSE}
library(xaringanthemer)

style_duo(
  primary_color = "#1F4257",
  secondary_color = "#F97B64",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

# Window to the World

---
class: inverse, center, middle

# UNIT 1: Studying the Earth

# Chatper 4: Hot and Wet Equatorial Region

---


---


---


---
class: inverse, center, middle

# UNIT 2: Our Country, India
# Chapter 8: Our Government 

---

# Summing Up

- India is democracy, where people elect their own government. 

- There are three levels of government in Inida - the Central Goverment, the State Government and the Local Government. 

- The Parliamment is the highest law making body in the country. It consistes of the President, the Lok Sabha and the Rajya Sabha. 

- The President is the head of the country and the Prime Minsiter is the head of the government. 

- The State Legislative Assembly is the law-making body at the state level. 

- The law of the land the Constitution is protected by the Courts. The Supreme Court is the highest courts in the country. 


---
# Workout

## I. Define the following

1. election: a process by which a group of people chooses a person for a particular position. 

2. parliament: the main law making body of a country, it usually consists of the elected representatives of the people. 

3. democracy: a system of government in which people choose their rulers by voting for them. 

4. constitution: a set of rules on the basis of which a country is governed. 




---
# Answer the follwing questions in one or two sentences

1. What is the meaning of 'government'? 

Government is the elected body which governs or rules a country or a state. 

2. What is the functions of the Central Government? 

The main function of the Central Government is to take care of the welfare of the people. 

3. How is the President of India elected? 

The President is elected by the members of the Lok Sabha, the Rajya Sabha and the State Legislative Assembles. 

4. Why is the Rajya Sabha called a permanent house? 

The Rajya Sabha can never be dissolved, the one third memebr of the Rajya Sabha retire every two year, so the the Rajya is known as the permanent house? 


---

5. Name the two houses of the Statement Government. 

- The two houses of the Sate Government are Vidhan Sabha (The Legilative Assembly) and Vidhan Parishad (the Legislative Council)

6. What is the Constitution? 

The Constitution is a set of rules on the basis of which a country is governed. 

---
class: inverse, center, middle

# UNIT 4: The World We Live In
# Chapter 12: Changing Means of Communication

---

---
1. What is the meaning of communication? 

2. What is a smartphone

3. What is the advantage of the radio over newspaper as means of mass communication? 

4. Classify the different types of communication about which you read in this chapter, nder the follwoing heads

listening: radio
reading: newspaper
writing: letters
audio-visual: smart phone , television                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 

---

---
class: inverse, center, middle
# UNIT 4: The World We Live In
# Chapter 16: The United Nations

---
# Summing Up

- After two world wars, world leaders formed the United Nations Organization (UN) to
bring piece and security to the world

- Aims of UN includes stopping war, prtection of the environment and human rights and controlling poverty and disease. 

- The six organs of the UN are : the General Assembly, the Secretariat, the Security Council, the Economic and Social Council, the International Court of Justice and the Trusteeship Council. The Secretary- General is the highest office of the UN. 


- Some of the important special agencies of the UN are the UNICEF, FAO, WHO, UNESCO, ILO. 
---
# Exploring new words

human rights: the basic rights every human being is entitled to regardless of sex, race, religion, language and nationality. 
special agency: a body specially designed for a particular activity. 
veto: the power to say 'no' and reject a decision taken by others in the group. 


# Workout

1. United Nations Day is celebrated on __24th October.__ 

2. At present, the UN has __193__ members. 

3. The six organs of the UN are __the General Assembly, the Secretariat, The Security Council, the Economic and Social Council, the Intertional Court of Justice and the Trusteeship Council.__ 

4. The __veto__ power is given tot he five permanent members of the Security Counl to turn down proposals raised by other members. 

6. __UNESCO__ works to protect the cultural and ntaional heritage of the its member-countries. 


---

# Expand the following

1. WHO = The World Health Organization

2. UNICEF = The United Nations Intentional Children's Fund

3. UNESCO = The United Nations Educational, Scientific and Cultural Organization

4. UNO = The United Nations Organization

5. FAO = The Food and Agricultural Organization


---

# IV. Answer the following questions in one or two sentences

1. When was the United Nations formed? How many members does the UN have at present? 

The UN was formed on 24th October 1945. UN has 193 members at present. 

2. What is the function of the Secretariat? 
The members of the secretariat carry out the day-to-day work of the UN. 

3. Who is the Secretary-General? What is his/her role? 
Antonio Guterres is the present Secretary-General. He is responsible for fulfilling decisions taken by the various organs. 

--- 

4. Name the special agencies that work under the ECOSOC. 
The special agencies that work under the ECOSOC are

- The World Health Organization(WHO)
- 
- The United Nations Intentional Children's Fund (UNICEF)
- 
- The United Nations Educational, Scientific and Cultural Organization (UNESCO)
- 
- The Food and Agricultural Organization (FAO)
- The International Labour Organization (ILO)


5. What is the function of the FAO? 

This agency tries to ensure that every person in the world has food to eat. It helps farmers grow more food by providing them with better seeds, fertiliser, irrigation facilities and insecticides. It also supplies food to people affected by famines, natural disasters and war. 

---
# V. Answer the following questions in a paragraph. 

1. Why was the United Nations formed?


2. What are the aims of the UN? 
The aims of the UN are
- maintain peace and security around the world. 
- developing friendly relations among countries.
- promoting social progress, better living standards and human rights. 
- protecting the environment, increasing food productions, and disaster management. 
- curbing terrorism. 



3. Write a brief note on the Security Council. 

4. Has the UN been a success or a failure? Discuss with the help of examples. 

5. What has India's contribution to the UN been? Discuss. 




---


```{r}
# usethis::use_github_pages(branch = "main")
```


---
class: inverse, center, middle
Final Exam on 21st  March 2022 (Monday)

9am to 1030am 

370 572 3003

Ms. Lopamudra
lopa@srgsomr.org

Window on the World

---
class: inverse, center, middle
# Unit 1
# Chapter 5:The Hot Desert Region

---
class: inverse, center, middle
# Unit 1
# Chapter 6:  The Temperate Grassland Region

---
class: inverse, center, middle
# Unit 2
# Chapter 8: Our Government

---
class: inverse, center, middle
# Unit 2
# Chapter 9: Our Culture and Heritage

---
class: inverse, center, middle
# Unit 3
# Chapter 11: The Struggle for Independence

---
## Summing up

- Disapppointed by the British rule, a few educated Indians came forward to form the Indian National Congress in 1885. 

- In the beginning, the Congress made moderate demands like letting Indians join the government. However, later some members of the Indian National Congress started demanding swaraj, or self-rule. 

- To weaken the strength of the freedome struggle the British divided Bengal on the basis of religion. This led to Swadeshi Movement. 

- Gandhiji returned from South Africa in 1915 and joined the freedom struggle. 

- Gandhiji launched the Non-cooperation Movemenet in 1920. People boycotted British goods and students refused to attend schools and colleges. 

- Gandhiji launched the Civil Disobedience Movement in 1930,with the Dandi March. 

- The Quit India Movement of 1942 showed the world how the British were suppressing the Indians.


---
## Summing up contd....

- World war II weakened the British.They were forced to leave India. 

- Before they left, the British divided India into two countries-India and Pakistan-on the basis of religion.

- India gained independence on 15 August 1947.


## Exploring new worlds

- swadeshi: things that are made in one's own country
- swaraj: self-rule
- patriotism: a strong love for, or attachment to, one's homeland. 
- World War I: a war that took place between 1914 and 1918 involving many countries from Europe, North America and Asia, causing the deaths of about nine million people
- satyagraha: a form of non-voilent protest in which truth is the main force
- lathi-charge: to use lathis or sticks to hit people in a crowd, so as to scatter them
-World War II: another war that took place between 1939 and 1945, involving the many countries around the world, resulting in the death of over 50 million people. 

---
## Fill in the blanks

1. in 1905, the British partitioned _**Bengal**_ on the basis of _**religion**_. 

2. _**Swadeshi**_ means made in one's own country. 


3.World war I broke out in _**1914**_.

4.Mahatma Gandhi come back to india from _**south Africa**_.He used  _** Satyagraha**_  to fight British.

5.Gandhiji launched the _**Civil Disobedience**_ Movement eith the Dandi March.

6.The leader of the Muslim League, _**Mohammad Ali Jinnah**_ demanded a separate state for the Muslims,to be called _**Pakistan**_.

---
## Choose the correct answer

1. One of the members of the Indian National Congress who demande. 

a. Gopal Krisha Gokhale

**b. Bal Gangadhar Tilak**

c. Bhagat Singh

d. Dadabhai Naoroji


2. Gandhiji came back to India in _____

a. 1914

**b. 1915**

c. 1919

d. 1930

---

3.The Swadeshi Movement led to____________;

**a.people refuse to use British goods**

b. the division of Bengal 

c.Both 'a' and 'b'

d.freedom from British rule

4.People had gathered peacefully at Jalllianwalla Bagh to protest against the _____________.

**a.Rowlatt Act**

b.Government of Indian Act

c.Partition of India into India and Pakistan

d capture of Bhagat Singh.

5. India because independence on _______.

a.15 August 1945

b. 26 January 1950

**c. 15 August 1947**

d.26 August 1945

---
## Aswer the following question in one or two sentence
1.Who said “ Freedom is my birth right and I shall have it.”?

Ans-Bal Gangadhar Tilak said “ Freedom is my birth right and I shall have it.”

2.Why did British want to divide Bengal?

Ans-To suppress the growing unity of Indians,Britishers decided to divide Bengal which was the main centre of nationalist movement.

3.How did British treat India after World War I?

Ans-Many Indian soldiers lost their lives in world war I while fighting for Britain. Despite this the British became harsher towards the Indians and imposed more taxes to recover their
loss incurred in the war.

4.How did Gandhiji returned to India after the freedom struggle?

Ans-In 1915, Gandhi returned back to India from South Africa. Soon he became one of the main leaders of the Indian freedom struggle.Under his leadership,the freedom struggle
reached to every nook and corner of India.

---
5.What was the Rowlatt Act? 

Ans-The British passed the Rowlatt act in 1919.According to this act British officers were allowed to arrest anybody they suspected, without presenting the case in the court(Trial).

6.What is the meaning of Satyagraha?

Ans-Satyagraha is a form of non-violent protest in which truth is the main force.

7.Why was the non cooperation movement withdrawn?

Ans-In 1920, Gandhi announced a peaceful Non-cooperation movement but he withdrew the movement in 1922 as it turned violent in some places.

8.What is Khadi ? Why did Gandhiji ask people to use Khadi?

Ans-The rough hand woven cloth is called Khadi.Gandhiji asked people to stop using cloth made in England and use Khadi. According to him India can save crores of rupees in a
year. Not only that but can generate employment opportunities for Indians.

9.When did India finally become independent? 

Ans-After centuries of foreign rule and years of struggle, India finally became an Independent country on 15th August 1947.



